This is an example of article title

### 2025-10-28 paper/paper.tex
Finish refactor footnotes- and adding a note of left/right actions.

\verb|identity_element(G)| or \verb|identity_element(G, typeof(g))|, where \verb|g| is an element of the group. The first variant will always generate a point in the default representation of the group, while the latter will generate a point in the same representation as \verb|g|.%
\footnote{The in-place variant \texttt{identity\_element!(G, e::T)} infers the representation from the type \texttt{T} of \texttt{e}.}

@@

\subsubsection*{Topological basics.}
Given a Lie group \verb|G|, we obtain the Lie algebra by calling $\frak g$ \verb|= LieAlgebra(G)|.
To access the Lie group again, use \verb|base_lie_group(|$\frak g$\verb|)|. Similarly \verb|base_manifold(|$\frak g$\verb|)| returns the underlying manifold of the Lie group.\\
As a technical detail, the Lie algebra is modelled as a tangent space\footnote{see the documentation of~\href{https://juliamanifolds.github.io/ManifoldsBase.jl/stable/metamanifolds/\#ManifoldsBase.TangentSpace}{ManifoldsBase.TangentSpace}} using the already mentioned \verb|Identity(G)| as base point.
A zero vector is generated via \verb|zero_vector(|$\frak g$\verb|)| for the default representation and \verb|zero_vector(|$\frak g$\verb|, T)| for a specific representation type \verb|T|.\footnote{the in-place variant \texttt{zero\_vector!($\frak g$, X::T)} can infer the type \texttt{T} of \texttt{X} automatically.}

@@

Given a vector $c \in \mathbb R^n$, we obtain the tangent vector by calling \verb|get_vector(|$\frak g$\verb|, c, b)| where \verb|b| is a basis of the tangent space, i.e.\ a subtype of \verb|AbstractBasis| and defaults within \verb|LieGroups.jl| to \verb|DefaultLieAlgebraOrthogonalBasis()|.
When a Lie group has different representations of points and tangent vectors, these are distinguished by calling \verb|get_vector(|$\frak g$\verb|, c, b, T)| specifying the tangent vector type
\footnote{the in-place variant \texttt{get\_vector!($\frak g$, X::T, c, b)} can infer the type \texttt{T} of \texttt{X} directly.}
Given a tangent vector $X \in \frak g$, we obtain its coordinates by calling \verb|get_coordinates(|$\frak g$\verb|, X, B)|%
%\footnote{in-place variant \texttt{get\_coordinates!($\frak g$, c, X, b)}}
, where the Basis is again optional.

For the case of the default, the \verb|DefaultLieAlgebraOrthogonalBasis()| the more commonly used names \verb|hat(|$\frak g$\verb|, c)|\footnote{in-place variant \texttt{hat!($\frak g$, X::T, c)}} (again with an optional vector type \verb|T|) and \verb|vee(|$\frak g$\verb|, X)|\footnote{in-place variant \texttt{vee!($\frak g$, c, X)}} are implemented

\subsubsection*{Push forward and pull back of tangent vectors}
To the representation of a tangent vector $X \in \frak g$ to be represented in the tangent space at $g \in \mathcal G$ we have to use the push forward of the left multiplication with $g$, i.e.\ $D\lambda_g(e)[X]$. This is implemented as \verb|push_forward_tangent(G, g, X)|\footnote{in-place variant \texttt{push\_forward\_tangent!(G, Y, g, X)}.}
Conversely, to represent a tangent vector $Y \in T_g\mathcal G$ back in the Lie algebra $\frak g$, we have to use the pull back of the left multiplication with $g^{-1}$, i.e.\ $D\lambda_{g^{-1}}(g)[Y]$. This is implemented as \verb|pull_back_tangent(G, g, Y)|\footnote{in-place variant \texttt{pull\_back\_tangent!(G, X, g, Y)}.}

@@

Currently for both \verb|exp| as well as \verb|conjugate|, the Jacobian is implemented. Note that for \verb|exp|, the domain is the Lie algebra. Since that is a vector space, its tangent space(s) can be identified with the Lie algebra again. Hence both Jacobians are maps from the Lie algebra to itself. The signatures are
\verb|jacobian_exp(G, p, X, b)|\footnote{in-place variant \texttt{jacobian\_exp!($\frak g$, J, p, X, b)}} and \verb|jacobian_conjugate(G, g, X, b)|\footnote{in-place variant \texttt{jacobian\_conjugate!($\frak g$, J, g, X, b)}}, where \verb|b| is again the basis to represent the tangent vectors in coordinates and defaults to \verb|DefaultLieAlgebraOrthogonalBasis()|.

@@

the main functions then are \verb|apply(a::GroupAction, g, p)|%
\footnote{in-place variant \texttt{apply!(a::GroupAction, q, g, p)}.}
to compute \(\sigma(g, p)\) for a group action \verb|a|, where $g\in \mathcal G$ and $p \in \mathcal M$, as well as its differential \verb|diff_apply(a::GroupAction, g, p, X)|%
\footnote{in-place variant \texttt{diff\_apply!(a::GroupAction, Y, g, p, X)}.}
to compute \(D\sigma(g, p)[X]\) for a tangent vector \(X \in T_p\mathcal M\) with respect to the manifold argument as well as \verb|diff_group_apply(a::GroupAction, g, p, Y)|%
\footnote{in-place variant \texttt{diff\_group\_apply!(a::GroupAction, Z, g, p, Y)}.}
to compute \(D\sigma(g, p)[Y]\) for a Lie algebra element \(Y \in \frak g\).

@@

{\color{red} TODO: Discuss left and right group actions here?}

@@

\section{An example how to use {\texttt{LieGroups.jl}}}\label{sec:Example}
\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%

>>>>

\verb|identity_element(G)| or \verb|identity_element(G, typeof(g))|, where \verb|g| is an element of the group. The first variant will always generate a point in the default representation of the group, while the latter will generate a point in the same representation as \verb|g|%
%\footnote{The in-place variant \texttt{identity\_element!(G, e::T)} infers the representation from the type \texttt{T} of \texttt{e}.}
.

@@

\subsubsection*{Topological basics.}
Given a Lie group \verb|G|, we obtain the Lie algebra by calling $\frak g$ \verb|= LieAlgebra(G)|.
To access the Lie group again, use \verb|base_lie_group(|$\frak g$\verb|)|. Similarly \verb|base_manifold(|$\frak g$\verb|)| returns the underlying manifold of the Lie group.\\
As a technical detail, the Lie algebra is modelled as a tangent space\footnote{see the documentation of~\href{https://juliamanifolds.github.io/ManifoldsBase.jl/stable/metamanifolds/\#ManifoldsBase.TangentSpace}{ManifoldsBase.TangentSpace}} using the already mentioned \verb|Identity(G)| as base point.
A zero vector is generated via \verb|zero_vector(|$\frak g$\verb|)| for the default representation and \verb|zero_vector(|$\frak g$\verb|, T)| for a specific representation type \verb|T|%
%\footnote{the in-place variant \texttt{zero\_vector!($\frak g$, X::T)} can infer the type \texttt{T} of \texttt{X} automatically.}
.

@@

Given a vector $c \in \mathbb R^n$, we obtain the tangent vector by calling \verb|get_vector(|$\frak g$\verb|, c, b)| where \verb|b| is a basis of the tangent space, i.e.\ a subtype of \verb|AbstractBasis| and defaults within \verb|LieGroups.jl| to \verb|DefaultLieAlgebraOrthogonalBasis()|.
When a Lie group has different representations of points and tangent vectors, these are distinguished by calling \verb|get_vector(|$\frak g$\verb|, c, b, T)| specifying the tangent vector type%
%\footnote{the in-place variant \texttt{get\_vector!($\frak g$, X::T, c, b)} can infer the type \texttt{T} of \texttt{X} directly.}
.
Given a tangent vector $X \in \frak g$, we obtain its coordinates by calling \verb|get_coordinates(|$\frak g$\verb|, X, B)|%
%\footnote{in-place variant \texttt{get\_coordinates!($\frak g$, c, X, b)}}
, where the Basis is again optional.

For the case of the default, the \verb|DefaultLieAlgebraOrthogonalBasis()| the more commonly used names \verb|hat(|$\frak g$\verb|, c)|
%\footnote{in-place variant \texttt{hat!($\frak g$, X::T, c)}}
(again with an optional vector type \verb|T|) and \verb|vee(|$\frak g$\verb|, X)|
%\footnote{in-place variant \texttt{vee!($\frak g$, c, X)}}
are implemented

\subsubsection*{Push forward and pull back of tangent vectors}
To the representation of a tangent vector $X \in \frak g$ to be represented in the tangent space at $g \in \mathcal G$ we have to use the push forward of the left multiplication with $g$, i.e.\ $D\lambda_g(e)[X]$. This is implemented as \verb|push_forward_tangent(G, g, X)|%
%\footnote{in-place variant \texttt{push\_forward\_tangent!(G, Y, g, X)}.}
.
Conversely, to represent a tangent vector $Y \in T_g\mathcal G$ back in the Lie algebra $\frak g$, we have to use the pull back of the left multiplication with $g^{-1}$, i.e.\ $D\lambda_{g^{-1}}(g)[Y]$. This is implemented as \verb|pull_back_tangent(G, g, Y)|%
%\footnote{in-place variant \texttt{pull\_back\_tangent!(G, X, g, Y)}.}
.

@@

Currently for both \verb|exp| as well as \verb|conjugate|, the Jacobian is implemented. Note that for \verb|exp|, the domain is the Lie algebra. Since that is a vector space, its tangent space(s) can be identified with the Lie algebra again. Hence both Jacobians are maps from the Lie algebra to itself. The signatures are
\verb|jacobian_exp(G, p, X, b)|
%\footnote{in-place variant \texttt{jacobian\_exp!($\frak g$, J, p, X, b)}}
and \verb|jacobian_conjugate(G, g, X, b)|%
%\footnote{in-place variant \texttt{jacobian\_conjugate!($\frak g$, J, g, X, b)}}
, where \verb|b| is again the basis to represent the tangent vectors in coordinates and defaults to \verb|DefaultLieAlgebraOrthogonalBasis()|.

@@

the main functions then are \verb|apply(a::GroupAction, g, p)|
%\footnote{in-place variant \texttt{apply!(a::GroupAction, q, g, p)}.}
to compute \(\sigma(g, p)\) for a group action \verb|a|, where $g\in \mathcal G$ and $p \in \mathcal M$, as well as its differential \verb|diff_apply(a::GroupAction, g, p, X)|
%\footnote{in-place variant \texttt{diff\_apply!(a::GroupAction, Y, g, p, X)}.}
to compute \(D\sigma(g, p)[X]\) for a tangent vector \(X \in T_p\mathcal M\) with respect to the manifold argument as well as \verb|diff_group_apply(a::GroupAction, g, p, Y)|
%\footnote{in-place variant \texttt{diff\_group\_apply!(a::GroupAction, Z, g, p, Y)}.}
to compute \(D\sigma(g, p)[Y]\) for a Lie algebra element \(Y \in \frak g\).

@@

Note that while the group action $\sigma(g, \sigmaæ(h, p)) = \sigma(g \cdot h, p)$ “appends” a new action (w.r.t.~$g$) on the left, for the inverse we have
\begin{align*}
        \sigma^{-1}(g, \sigma^{-1}(h, p))
        &= \sigma(g^{-1}\cdot h^{-1}, p)
        = \sigma((h \cdot g)^{-1}, p)
        \\
        &= \sigma^{-1}(h \cdot g, p)
\end{align*}
for all \(g, h \in \mathcal{G}\). This is a so-called right action.
Similarly for a right group action the inverse is a left group action.
This is tanken into account when using \verb|apply|.

@@

\section{An example how to use {\texttt{LieGroups.jl}}}\label{sec:Example}

{\color{red}TODO: Brainstorm over one or two examples with code.}
\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%
